Individualized Measures of Partisan Fairness and Utility in Redistricting (??)

### 2021-08-29 paper/paper.Rmd
fix math error

```{=tex}
\begin{restatable}{prop}{propglobal} \label{prop:global}
Let $\{s_p:p\in P\}$ be a set of party popular vote shares, and $f:[0,1]\bijto[0,1]$ be a rule for assigning each party a share of seats according to their share of the overall vote.
Define the total utility for this rule as \[
    U_e^{(G)}(f) = \sum_{v\in V} h\qty(f\qty(s_{\vote_e(v)})).
\] 
Then if $h$ is convex, $U_e^{(G)}$ is maximized for $f(x)=\ind\{x\ge \half\}$, and if $h$ is concave, $U_e^{(G)}$ is maximized by an increasing $f$.
In particular, if $h(x)=\log(x)$ and every party receives at least one vote, then $f(x)=x$ maximizes $U_e^{(G)}$.

>>>>

```{=tex}
\begin{restatable}{prop}{propglobal} \label{prop:global}
Let $S=\{s_p:p\in P\}$ be a set of party popular vote shares, and $f:[0,1]\bijto[0,1]$ be a rule for assigning each party a share of seats according to their share of the popular vote.
Define the total utility for this rule as \[
    U_e^{(G)}(f) = \sum_{v\in V} h\qty(f\qty(s_{\vote_e(v)})).
\] 
Then if $h$ is convex, $U_e^{(G)}$ is maximized for $f(x)=\ind\{x\ge \max S\}$, and if $h$ is concave, the maximizer of $U_e^{(G)}$ will be an increasing function.
In particular, if $h(x)=\log(x)$ and every party receives at least one vote, then $f(x)=x$ maximizes $U_e^{(G)}$.
